---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
I loaded the data and transformed it into a table.
```{r}

library(tidyverse)
data <- read.csv("activity.csv")
print(data)
```





## What is mean total number of steps taken per day?
```{r}
datasum <- data %>% 
group_by(date) %>% 
summarise(summatory=sum(steps))
print(datasum)

```
```{r}
hist(datasum$summatory)
```
I made an hinstrogram of the frequency and the steps.


## What is the average daily activity pattern?

```{r}
mean(datasum$summatory, na.rm = TRUE) 
median(datasum$summatory, na.rm = TRUE)
x <- min(datasum$summatory, na.rm = TRUE) 
```
I calculated the mean and the median.

## Imputing missing values
```{r}
data[is.na(data$steps),]
nrow(data[is.na(data$steps),])
```
I fill the missing values so there aren't NA.

```{r}
data[is.na(data$steps),1] <- x
print(data)
```

```{r}
datasum <- data %>% 
group_by(date) %>% 
summarise(summatory=sum(steps))
print(datasum)
```
```{r}
hist(datasum$summatory)
```
```{r}
mean(datasum$summatory, na.rm = TRUE) 
median(datasum$summatory, na.rm = TRUE)
```
I calculated the mean and median again.
The values changed.


## Are there differences in activity patterns between weekdays and weekends?

```{r}
library(chron)
data$weekend  <- as.factor(is.weekend(data$date))

```
```{r}
library(lattice)
stepsByDay <- aggregate(data$steps ~ data$interval + data$weekend, data, mean)
colnames(stepsByDay) <- c("steps", "weekend", "interval")
xyplot(steps ~ interval | weekend, stepsByDay, type = "l", layout = c(1, 2), 
    xlab = "Interval", ylab = "Number of steps")
```

